### 2020-03-01 Thesis-Chapter2-Background.tex
Add \my{chap/sec/fig/tab} commands
Add some new sources

These arguments are introduced here and analyzed in detail in Chapter \ref{chap-arguments}.

@@

\begin{itemize}
    \item Reject EA until technical capabilities are ready \cite{varia_2018}
    \item Be forthcoming with data so that we know what to work on \cite{armerding_2017}
    \item Don't prescribe technical methods, but be clear about principles \cite{matyas_incommensurability_2018}
    \item Fund the research \cite{varia_2018}
\end{itemize}

>>>>

These arguments are introduced here and analyzed in detail in \mychap{chap-arguments}.

@@

\begin{itemize}
    \item Reject EA until technical capabilities are ready \cite{varia_2018}
    \item Be forthcoming with data so that we know what to work on \cite{devlin_2018}
    \item Don't prescribe technical methods, but be clear about principles \cite{matyas_incommensurability_2018}
    \item Fund the research \cite{varia_2018}
\end{itemize}
